Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-06 manuscript/manuscript.Rmd
rewrote a bit

Your text comes here. Separate text sections with \cite{Mislevy06Cog}.

@@

>>>>

<!-- Your text comes here. Separate text sections with \cite{Mislevy06Cog}. -->

@@

# Reinforcement learning {#sec:DRL}

Reinforcement learning (RL) is a way of approaching *control problems* through machine learning.
An RL application can be conceptually separated into two parts: an *agent*, and an *environment*.
The *environment* is commonly a computer simulation.
The *agent*, on the other hand, is a computer program which interacts with the environment.
That is, the agent may act on the environment and change its state.
Such an action and its consequence, moreover, give the agent a *reward* which encodes our goal for the agent.
The main part of an RL algorithm is then to progressively improve the agent's *policy*, in order to maximize the cumulative reward received. 
This is done by aggregating experience and learning from it.

In our case, the environment will be a computational model of the population dynamics of a fishery.
The agent chooses how much to fish from a given species in the environment, thereby changing the populations in the environment's state.

\begin{align}
a^2+b^2=c^2
\end{align} -->
